%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Twenty Seconds Resume/CV
% LaTeX Template
% Version 1.0 (14/7/16)
%
% Original author:
% Carmine Spagnuolo (cspagnuolo@unisa.it) with major modifications by 
% Vel (vel@LaTeXTemplates.com) and Harsh (harsh.gadgil@gmail.com)
%
% License:
% The MIT License (see included LICENSE file)
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[letterpaper]{twentysecondcv} % a4paper for A4

% Command for printing skill overview bubbles
\newcommand\skills{ 
~
	\smartdiagram[bubble diagram]{
        \textbf{Software}\\\textbf{Engineering},
        \textbf{~~~~~~DevOps~~~~~~},
        \textbf{Networks},
        \textbf{~~~~~Linux~~~~~},
        \textbf{~~~~~CI/CD~~~~~},
        Scrum\\Master,
        \textbf{~~~~~~Git~~~~~~}
    }
}

% Programming skill bars
\programming{{C $\textbullet$  SQL $\textbullet$ Terraform $\textbullet$ \large \LaTeX / 1}, {Bash $\textbullet$ Groovy / 2}, {Python / 5}}

% Projects text
\education{
\textbf{MSc., Automatics \& Robotics} (GPA: 5.0) \\
Spec.: Computer Control Systems / Neurocybernetics \\
AGH University of Science \& Technology \\
2015 - 2017 | Kraków, Poland

\textbf{BSc., Automatics \& Robotics} (GPA: 4.5) \\
AGH University of Science \& Technology \\
2011 - 2015 | Kraków, Poland
}

%----------------------------------------------------------------------------------------
%	 PERSONAL INFORMATION
%----------------------------------------------------------------------------------------
% If you don't need one or more of the below, just remove the content leaving the command, e.g. \cvnumberphone{}

\cvname{ŁUKASZ DUDEK} % Your name
\cvjobtitle{ Software Engineer } % Job title/career

\cvlinkedin{/in/ljbdudek}
\cvgithub{LJBD}
\cvnumberphone{(+48) 663361144} % Phone number
\cvsite{} % Personal website
\cvmail{ljbdudek@gmail.com} % Email address

%----------------------------------------------------------------------------------------

\begin{document}

\makeprofile % Print the sidebar

\section{About me}

An automation \& open-sourceness enthusiast, I'm an all-round software engineer curious about every aspect of technology stacks in front of me.
I love devising \& discussing improvements, both for software and processes.
Being a good team player, I care about the quality of communication with those around me.

%----------------------------------------------------------------------------------------
%	 EXPERIENCE
%----------------------------------------------------------------------------------------

\section{Experience}

\begin{twenty} % Environment for a list with descriptions
\twentyitem
    	{Oct 2017 -}
		{Present}
        {DevOps/QA Engineer}
        {\href{http://www.silvair.com/}{Silvair}}
        {}
        {\begin{itemize}
        \item Designing \& developing CI/CD pipelines in Jenkins for embedded firmware teams.
        \item Designing \& developing automation tools in Python 3.5+ across the technology stack (from hardware utilities, through systems administration to web platform clients).
        \item Raising Python code quality in the entire company (unit tests, PyLint, black, Sphinx).
        \item Introducing good DevOps practices.
        \item Acting as a Scrum Master in a small team.
        \\\\
        \textbf{Tools:} Jenkins, Docker, AWS (S3, EC2, Athena), Debian/Ubuntu, Behave, Flask, Terraform, GitHub, Jira
        \end{itemize}}
        \\
	\twentyitem
    	{Jan 2015 -}
		{Aug 2017}
        {Control Systems Engineer}
        {\href{http://www.synchrotron.uj.edu.pl/en}{NRSC SOLARIS, Jagiellonian University}}
        {}
        {
        {\begin{itemize}
        \item Managing distributed control systems based on TANGO Controls framework and its services (eg. archiving, supervision, back-end diagnostics).
        \item Designing and writing device drivers \& client applications in Python 2.7/3.5 for a distributed control system.
        \item Participating in open-source projects across Europe, co-authoring talks \& posters for conferences.
        \item Introducing good team practises and programming styles.
    	\\\\
    	\textbf{Tools:} TANGO Controls, PyQt, MySQL, Jenkins, Docker, CentOS, VMWare, GitLab
    \end{itemize}}
        }
    \\   
    \twentyitem
   		{Aug 2016 -}
		{Dec 2016}
        {Software Engineer}
        {\href{http://www.eaiib.agh.edu.pl/}{AGH University of Science \& Technology}}
        {}
        {
        {\begin{itemize}
        \item Project: TANGO Controls Industralisation.
        \item Developing device drivers for industry protocols \& a SCADA application in Python 2.7.
        \\\\
        \textbf{Tools:} TANGO Controls, PyQt, OPC UA, Modbus, SCPI, BACNet-IP
    \end{itemize}}
        }
     \\
     \twentyitem
   		{Mar 2016 -}
		{Nov 2016}
        {Software Engineer}
        {\href{http://www.fais.uj.edu.pl/en\_GB/homepage}{Jagiellonian University}}
        {}
        {
        \begin{itemize}
        \item Project: StageEye - a prototype of a system positioning elements on a stage.
        \item Developing a laser driver \& a mobile application with web backend - all in Python 2.7.
        \\\\
        \textbf{Tools:} TANGO Controls, Flask, MongoDB, Kivy
    \end{itemize}
    	}
        
	%\twentyitem{<dates>}{<title>}{<location>}{<description>}
\end{twenty}

%----------------------------------------------------------------------------------------
%	 RESEARCH
%----------------------------------------------------------------------------------------

\end{document} 
